An assessment of photometric redshift PDF performance in the context of LSST

### 2018-09-02 paper/tex/results.tex
fixed figure sizes
add scotts rule smoothing to Figure 4

\begin{figure*}
%\centering
\includegraphics[width=0.49\textwidth]{fig/pz_12codes_261931_crop.jpg}\includegraphics[width=0.5\textwidth]{fig/pz_12codes_471167_crop.jpg}\\
\includegraphics[width=\textwidth]{fig/pz_12codes_713178_crop.jpg}\includegraphics[width=\textwidth]{fig/pz_12codes_982747_crop.jpg}
\caption{Four illustrative examples of individual p(z) distributions produced by the codes.  The red vertical line represents the true redshift.  Examples are chosen with common features seen in PDFs: tight unimodal $p(z)$ (upper left), broad unimodal $p(z)$ (upper right), bimodal $p(z)$ (lower right), and complex/multimodal $p(z)$ (lower left).  Codes show varying amounts of small-scale structure in their reconstruction of the posterior distribution.  We see varying responses from the codes in the presence of color degeneracies and photometric errors, resulting in narrow and broad unimodal, bimodal, and multi-modal $p(z)$ curves.} \label{fig:pz_examples}
\end{figure*}

@@

\begin{table}
\setlength{\tabcolsep}{2pt}
\centering
\caption{The fraction of ``catastrophic outlier'' PIT values.  We expect a value of 0.0002 for a proper Uniform distribution.  An excess over this small value indicates true redshifts that fall outside the non-zero support of the $p(z)$.  }\label{tab:pitoutlier}
\begin{tabular}{lc}
\hline
\hline
 ``catastrophic outlier''\\ PIT fraction\\
\hline
Photo-z Code & fraction PIT$<10^{-4}$ or $>$0.9999\\
\hline
\textsc{ANNz2} & 0.0265\\
\textsc{BPZ} & 0.0192\\
\textsc{Delight} & 0.0006\\
\textsc{EAZY} & 0.0154\\
\textsc{FlexZBoost} & 0.0202\\
\textsc{GPz} & 0.0068\\
\textsc{LePhare} & 0.0486\\
\textsc{METAPhoR}& 0.0229\\
\textsc{CMNN} & 0.0034\\
\textsc{Skynet} & 0.0001\\
\textsc{TPZ} & 0.0130\\
\hline
\textsc{TrainZ} & 0.0002\\
\end{tabular}
\end{table}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{fig/NZsumplot_12codes.jpg}
\caption{The stacked $p(z)$ produced by each photo-$z$ code ($\hat{N}(z)$, red) compared to the spectroscopic redshift distribution ($N'(z)$, blue).  Varying levels of small-scale structure are seen in the codes.  $N'(z)$ is smoothed using a single bandwidth chosen via Scott's rule for all codes.} \label{fig:nz}
%\aim{Arguably this could also be clarified by showing the true $n'(z)$ once and then differences from it for each cod's stacked estimator\dots}\scc{what if we plot the difference between true and stacked rather than soverposing the two lines? Sam please do not hate me.}
\end{figure*}

@@

\begin{table}  %%% DATA TABLE %%%
\centering
\caption{CDE loss statistic for each photo-$z$ code.} \label{tab:cdeloss}
\begin{tabular}{lr}
\hline
\bf Photo-$z$ Code & \bf CDE Loss \\
\hline
\textsc{ANNz2} 		& $-6.88$ \\
\textsc{BPZ} 		& $-7.82$ \\
%\textsc{Delight} 	& $-4.06$ \\
\textsc{Delight}    & $-8.33$\\
%\textsc{EAZY} 		& $-7.97$ \\
\textsc{EAZY}       & $-7.07$ \\
%\textsc{FlexZBoost} & $-11.51$ \\
\textsc{FlexZBoost} & $-10.60$\\
\textsc{GPz} 		& $-9.56$ \\
\textsc{LePhare} 	& $-1.66$ \\
\textsc{METAPhoR} 	& $-6.28$ \\
%\textsc{CMNN} 		& $-$ \\
\textsc{CMNN}         & $-10.43$ \\
\textsc{SkyNet} 	& $-7.89$ \\
\textsc{TPZ} 		& $-9.55$ \\
\hline
\trainz		& $-0.83$ \\
%\textsc{Frankenz}	& $-$  \\
%\hline
\end{tabular}
\end{table}

\begin{table}
\setlength{\tabcolsep}{2pt}
\begin{center}
\caption{Root-Mean-Square-Error (RMSE) statistics for the eleven photo-z codes for both PIT and $\hat{N}(z)$ distributions.}\label{tab:rmse}
\begin{tabular}{lcc}
\hline
\hline
Root-Mean-Square-Error \\
(RMSE) statistics \\
\hline
Photo-z Code & PIT RMSE & N(z) RMSE\\
\hline
\textsc{ANNz2}      & 0.019 & 0.0054\\
\textsc{BPZ}        & 0.032 & 0.0050\\
\textsc{Delight}    & 0.111 & 0.0056\\
\textsc{EAZY}       & 0.054 & 0.0102\\
\textsc{FlexZBoost} & 0.021 & 0.0022\\
\textsc{GPz}        & 0.048 & 0.0042\\
\textsc{LePhare}    & 0.028 & 0.0062\\
\textsc{METAPhoR}   & 0.064 & 0.0081\\
\textsc{CMNN}         & 0.108 & 0.0009\\
\textsc{Skynet}     & 0.054 & 0.0144\\
\textsc{TPZ}        & 0.082 & 0.0031\\
\hline
\trainz		& 0.0025 & 0.0013\\
\end{tabular}
\end{center}
\end{table}

@@

\begin{table}
\setlength{\tabcolsep}{2pt}
\caption{Moments of the stacked $\hat{N}(z)$ distribution}\label{tab:moments}
\begin{tabular}{lccc}
\hline
\hline
 \multicolumn{4}{l}{Stacked $n(z)$ Moments} \\
\hline
              & 1st Moment & 2nd Moment & 3rd Moment \\
\textsc{Truth}     & 0.701      &   0.630    & 0.671  \\
\hline
Photo-z Code       & 1st Moment & 2nd Moment & 3rd Moment\\
\hline
\textsc{ANNz2}     & 0.702      & 0.625      & 0.653    \\
\textsc{BPZ}       & 0.699      & 0.629      & 0.671    \\
\textsc{Delight}   & 0.692      & 0.609      & 0.638    \\
\textsc{EAZY}      & 0.681      & 0.595      & 0.619    \\
\textsc{FlexZBoost}& 0.694      & 0.610      & 0.631    \\
\textsc{GPz}       & 0.692      & 0.605      & 0.619    \\
\textsc{LePhare}   & 0.718      & 0.668      & 0.741    \\
\textsc{METAPhoR}  & 0.705      & 0.628      & 0.657    \\
\textsc{CMNN}        & 0.701      & 0.628      & 0.667    \\
\textsc{Skynet}    & 0.743      & 0.708      & 0.797    \\
\textsc{TPZ}       & 0.700      & 0.619      & 0.643    \\
\hline
\trainz	   & 0.699 		& 0.627 	& 0.666 \\
\end{tabular}
\end{table}

>>>>

\begin{figure*}
%\centering
\includegraphics[width=0.49\textwidth]{fig/pz_12codes_261931_crop.jpg}\includegraphics[width=0.5\textwidth]{fig/pz_12codes_471167_crop.jpg}\\
\includegraphics[width=0.49\textwidth]{fig/pz_12codes_713178_crop.jpg}\includegraphics[width=0.49\textwidth]{fig/pz_12codes_982747_crop.jpg}
\caption{Four illustrative examples of individual p(z) distributions produced by the codes.  The red vertical line represents the true redshift.  Examples are chosen with common features seen in PDFs: tight unimodal $p(z)$ (upper left), broad unimodal $p(z)$ (upper right), bimodal $p(z)$ (lower right), and complex/multimodal $p(z)$ (lower left).  Codes show varying amounts of small-scale structure in their reconstruction of the posterior distribution.  We see varying responses from the codes in the presence of color degeneracies and photometric errors, resulting in narrow and broad unimodal, bimodal, and multi-modal $p(z)$ curves.} \label{fig:pz_examples}
\end{figure*}

@@

\begin{table}
\setlength{\tabcolsep}{2pt}
\centering
\caption{The fraction of ``catastrophic outlier'' PIT values.  We expect a value of 0.0002 for a proper Uniform distribution.  An excess over this small value indicates true redshifts that fall outside the non-zero support of the $p(z)$.  }\label{tab:pitoutlier}
\begin{tabular}{lc}
\hline
\hline
 ``catastrophic outlier''\\ PIT fraction\\
\hline
Photo-z Code & fraction PIT$<10^{-4}$ or $>$0.9999\\
\hline
\textsc{ANNz2} & 0.0265\\
\textsc{BPZ} & 0.0192\\
\textsc{Delight} & 0.0006\\
\textsc{EAZY} & 0.0154\\
\textsc{FlexZBoost} & 0.0202\\
\textsc{GPz} & 0.0058\\
\textsc{LePhare} & 0.0486\\
\textsc{METAPhoR}& 0.0229\\
\textsc{CMNN} & 0.0034\\
\textsc{Skynet} & 0.0001\\
\textsc{TPZ} & 0.0130\\
\hline
\textsc{TrainZ} & 0.0002\\
\end{tabular}
\end{table}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{fig/NZsumplot_12codes_scottsrule.jpg}
\caption{The stacked $p(z)$ produced by each photo-$z$ code ($\hat{N}(z)$, red) compared to the spectroscopic redshift distribution ($N'(z)$, blue).  Varying levels of small-scale structure are seen in the codes.  Both $\hat{N}(z)$ and $N'(z)$ are smoothed using a single bandwidth chosen via Scott's rule for all codes.} \label{fig:nz}
%\aim{Arguably this could also be clarified by showing the true $n'(z)$ once and then differences from it for each cod's stacked estimator\dots}\scc{what if we plot the difference between true and stacked rather than soverposing the two lines? Sam please do not hate me.}
\end{figure*}

@@

\begin{table}  %%% DATA TABLE %%%
\centering
\caption{CDE loss statistic for each photo-$z$ code.} \label{tab:cdeloss}
\begin{tabular}{lr}
\hline
\bf Photo-$z$ Code & \bf CDE Loss \\
\hline
\textsc{ANNz2} 		& $-6.88$ \\
\textsc{BPZ} 		& $-7.82$ \\
%\textsc{Delight} 	& $-4.06$ \\
\textsc{Delight}    & $-8.33$\\
%\textsc{EAZY} 		& $-7.97$ \\
\textsc{EAZY}       & $-7.07$ \\
%\textsc{FlexZBoost} & $-11.51$ \\
\textsc{FlexZBoost} & $-10.60$\\
\textsc{GPz} 		& $-9.93$ \\
\textsc{LePhare} 	& $-1.66$ \\
\textsc{METAPhoR} 	& $-6.28$ \\
%\textsc{CMNN} 		& $-$ \\
\textsc{CMNN}         & $-10.43$ \\
\textsc{SkyNet} 	& $-7.89$ \\
\textsc{TPZ} 		& $-9.55$ \\
\hline
\trainz		& $-0.83$ \\
%\textsc{Frankenz}	& $-$  \\
%\hline
\end{tabular}
\end{table}

\begin{table}
\setlength{\tabcolsep}{2pt}
\begin{center}
\caption{Root-Mean-Square-Error (RMSE) statistics for the eleven photo-z codes for both PIT and $\hat{N}(z)$ distributions.}\label{tab:rmse}
\begin{tabular}{lcc}
\hline
\hline
Root-Mean-Square-Error \\
(RMSE) statistics \\
\hline
Photo-z Code & PIT RMSE & N(z) RMSE\\
\hline
\textsc{ANNz2}      & 0.019 & 0.0054\\
\textsc{BPZ}        & 0.032 & 0.0050\\
\textsc{Delight}    & 0.111 & 0.0056\\
\textsc{EAZY}       & 0.054 & 0.0102\\
\textsc{FlexZBoost} & 0.021 & 0.0022\\
\textsc{GPz}        & 0.027 & 0.0042\\
\textsc{LePhare}    & 0.028 & 0.0062\\
\textsc{METAPhoR}   & 0.064 & 0.0081\\
\textsc{CMNN}         & 0.108 & 0.0009\\
\textsc{Skynet}     & 0.054 & 0.0144\\
\textsc{TPZ}        & 0.082 & 0.0031\\
\hline
\trainz		& 0.0025 & 0.0013\\
\end{tabular}
\end{center}
\end{table}

@@

\begin{table}
\setlength{\tabcolsep}{2pt}
\caption{Moments of the stacked $\hat{N}(z)$ distribution}\label{tab:moments}
\begin{tabular}{lccc}
\hline
\hline
 \multicolumn{4}{l}{Stacked $n(z)$ Moments} \\
\hline
              & 1st Moment & 2nd Moment & 3rd Moment \\
\textsc{Truth}     & 0.701      &   0.630    & 0.671  \\
\hline
Photo-z Code       & 1st Moment & 2nd Moment & 3rd Moment\\
\hline
\textsc{ANNz2}     & 0.702      & 0.625      & 0.653    \\
\textsc{BPZ}       & 0.699      & 0.629      & 0.671    \\
\textsc{Delight}   & 0.692      & 0.609      & 0.638    \\
\textsc{EAZY}      & 0.681      & 0.595      & 0.619    \\
\textsc{FlexZBoost}& 0.694      & 0.610      & 0.631    \\
\textsc{GPz}       & 0.696      & 0.615      & 0.639    \\
\textsc{LePhare}   & 0.718      & 0.668      & 0.741    \\
\textsc{METAPhoR}  & 0.705      & 0.628      & 0.657    \\
\textsc{CMNN}        & 0.701      & 0.628      & 0.667    \\
\textsc{Skynet}    & 0.743      & 0.708      & 0.797    \\
\textsc{TPZ}       & 0.700      & 0.619      & 0.643    \\
\hline
\trainz	   & 0.699 		& 0.627 	& 0.666 \\
\end{tabular}
\end{table}
